Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal distribution

### 2018-05-24 manuscript.tex
Modif Sect 2 and 3
Rephrasing of Section 2 and 3

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the asymmetry, or the skewness, of the distribution. Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $Y = y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a \emph{standard} Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}
 and $\alpha \in \mathbb R$ is the skewness parameter which quantifies the asymmetry of the SN.  We then write $Y \sim SN(\xi, \omega^{2}, \alpha)$ to mean that the random variable $Y$ follows the noted SN distribution.
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.  A usual Normal distribution is the special case of the SN distribution when the skewness parameter, $\alpha$, is equal to 0.\footnote{This can be seen from Eq.~\eqref{def:snd_gen}.  If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0)$; this is the the probability a standard Normal random variable is less than or equal to 0, which is $0.5$.  The $0.5$ cancels with the $2$ in the denominator and what remains is the usual Normal density, $\frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$}
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
   \caption{Density function of a random variable $Y \sim SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types. Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
   \label{fig:SN.plot}
\end{figure}
%
For reasons related to the interpretation of the parameters in Eq.~\eqref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used, which is referred to as the \emph{centered parametrization} (CP).  We will be using the CP in this work, which includes a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$.  In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of the one used in the Equation~\eqref{def:snd_gen} with $(\xi, \omega^2, \alpha)$ by
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
\end{equation}
%
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$.

By using Eq.~\eqref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution (rather than simply a location and scale parameter) and $\gamma$ becomes an index for evaluating the skewness of the SN.

Beyond the mean of the SN, we introduce a second location parameter that will be largely used in the analyses: the median. The median of the SN, and in general the median of an absolute continuous random variable, is defined as that value $m$ such that 
%
\begin{equation} \label{eq:snmed}
\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2},
\end{equation}
%
where $SN(y;\xi, \omega, \alpha)$ follows Eq.~\eqref{def:snd_gen}.\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}

%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
0	&	 0.000 	&	1.000	&	 0.000 \\
2	&	 0.714	&	 0.491	&	 0.454\\
6	&	 0.787	&	 0.381	&	 0.891\\
10	&	 0.794	&	 0.370	&	 0.956\\
\hline
   \end{tabular}
   \caption{CP values, $(\mu, \sigma^2, \gamma)$, corresponding to the $\alpha$ values from Fig.~\ref{fig:SN.plot} (with location parameter $\xi = 0$ and scale parameter $\omega = 1$) using Eq.~\eqref{eq:snd_cp}.  Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{table}
%
Further details about the parametrization from Eq.~\eqref{def:snd_gen} (called \emph{Direct Parametrization} or DP), the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

%The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
The SN density shape is used to model the CCF.  In particular, using least-squares algorithm, we fit the following function:
%
\begin{eqnarray} \label{eq:3}
f_{CCF}(y_i) = \mathrm{C} - \mathrm{A} \times SN(y_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
\end{eqnarray}
%
where C is an unknown offset fitting the continuum of the CCF, A is an unknown amplitude parameter known with the term ``contrast'' and $y_1, \ldots, y_n$ are the set of RV's considered for the CCF. Note that the CCF is expressed in flux as a function of the lag of the cross-correlation template, expressed in RV.

Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution should in principle better catch this aspect, together with other changes in asymmetry, respect the Normal fit. To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars. The first star is Alpha Centauri b, whose CCF's have high signal-to-noise ratio (SNR). The second star is Corot-7, whose CCF's have low SNR. Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF, in particular as the SNR decreases.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{[1]HD128621Residuals.pdf} 
\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right). When looking at the residuals corresponding to the tails of the CCF, the results derived by the two fits are comparable. However, when focusing on the center of the CCF, the SN fit leads to slightly better results for both the stars. Moreover, as the SNR decreases, the SN distribution shows smaller residuals respect the Normal ones.}
    \label{fig:Residual.comparison}
\end{figure*}
%

In the following of the paper, we define RV as the mean of the Normal distribution. Concerning the fit of the CCF using the SN, we present at first $2$ indicators that define the RV of the star: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV (i.e. realling Eq.\eqref{eq:snmed}, $m$ = SN median RV). We will discuss advantages and limits for both these choices in Sec. \ref{sec:4} and Sec. \ref{sec:5}. For the width of the CCF, we use the FWHM of the Normal, which is $2\sqrt(2\ln2)\sigma$. The width of the SN, SN FWHM, is defined in the same way\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}. Being a Normal distribution symmetric, there is not such a parameter that evaluates the asymmetry of the distribution, so the BIS SPAN is used. The BIS SPAN will be compared to the asymmetric parameter $\gamma$ of the SN, known also as SN GAMMA. To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
%
\begin{equation}
R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
\label{eq:Pearson:corr}
\end{equation}
%
where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.  A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\%$ confidence interval for $R$ when needed.

@@

While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\eqref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM). The inclusion of the contrast parameter $A$ is justified by the expected behavior of the CCF in presence of active regions. Fig.~\ref{fig:spotA} shows that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width. This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
    \label{fig:spotA}
\end{figure*}
%

The reasons for including in Eq.~\eqref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}. We point out however that while the association between in this case BIS SPAN  (or $\gamma$) and FWHM (or SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.

@@

As final remark we recall that, when working with a linear regression, there are several ways to select the variables to include in the model. While usually the stepwise technique takes place \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\eqref{eq:RV:correction} that corrects from stellar activity is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it were the case, the matrix needed to calculate the estimates would have been singular, hence non invertible. This problem is known in statistic with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citep{belsley1991}. In the literature there are examples of stars presenting a high correlation between the contrast parameter $A$ and the FWHM \citep{Dumusque:2017aa,Feng:2017aa}. In the analyses of the presented work, we did not find any correlation between the contrast parameter $A$ and the FWHM (or between the contrast parameter $A$ and the SN FWHM) exceeding $0.66$ for all the analyzed stars and therefore the problem of multicollinearity is avoided. For the interpretation of the coefficients, we centered on the mean all the variables considered in the linear regression defined in Eq.~\eqref{eq:RV:correction}. Last, when proposing interactions between covariates, we found that only the one between the width and the asymmetry of the CCF is statistically helpful to explain spurious variations in RV's caused by stellar activity. Consequently, in the present work, the interaction between other variables are not used as covariates.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Simulation Study} \label{sec:soap}
In order to evaluate the performance of the proposed SN approach for modeling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\eqref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.

@@

Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae. In particular the $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN). We note also that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is not statistically significant to explain spurious variations caused by a faculae.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:faculae.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.0016$    & $0.26$ & $0.60$ \\
\hline
$\beta_{1}$            &    $3.75e-05$    & $0.0068$ & $0.0069$ \\
\hline
$\beta_{2}$            &     $7.79e-16$   &  $1.97e-05$ & $3.69e-08$\\
\hline
$\beta_{3}$            &     $0.25$   &  $0.0011$ & $0.0011$\\
\hline
$\beta_{4}$            &     $0.53$   &  $0.21$ & $0.21$\\
\hline
$R^{2}$      &     $0.9967$    &  $0.9571$ & $0.977$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\eqref{eq:RV:correction}. Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses. The term of interaction between the asymmetry and the width of the CCF is not helpful to explain part of the variability in the set of RV's. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
\label{table:faculae.test}
\end{table}

@@

As before, we corrected the originally estimated set of RV's by using Eq.~\eqref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:spot.test}. Also in this case the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the spot. The $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN). The main differences respect to the previous case are that the parameter $\beta_{3}$, associated with $\gamma$, and the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM), are statistically significant to explain spurious variations caused by a spot. This information could be useful in the future for disentangle spots from facuale.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\eqref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:spot.correction}
\end{figure*}

>>>>

The Skew Normal (SN) distribution is a class of probability distributions which includes the Normal distribution as a special case \citep{Azzalini1985}. The SN distribution has, in addition to a location and a scale parameter analogous to the Normal distribution's mean and standard deviation, a third parameter which describes the skewness of the distribution. Considering a random variable $Y\in \mathbb R$ (where $\mathbb R$ is the real line) which follows a SN distribution with location parameter $\xi \in \mathbb R$, scale parameter $\omega \in \mathbb R^{+}$ (i.e., the positive real line), and skewness parameter $\alpha \in \mathbb R$, its density at some value $y\in Y$ can be written as 
\begin{equation} \label{def:snd_gen}
SN(y;\xi, \omega, \alpha) = \frac{2}{\omega} \phi\left(\frac{y-\xi}{\omega}\right) \Phi\left(\frac{\alpha(y-\xi)}{\omega}\right),
\end{equation}
where $\phi$ and $\Phi$ are respectively the density function and the distribution function of a standard Normal distribution\footnote{A standard Normal distribution is a Normal distribution with a mean of 0 and a standard deviation of 1.}.
The skewness parameter $\alpha$ quantifies the asymmetry of the SN. 
Examples of SN densities under different skewness parameter values and the same location and scale parameters ($\xi = 0$ and $\omega = 1$) are displayed in Fig.~\ref{fig:SN.plot}.  A usual Normal distribution is the special case of the SN distribution when the skewness parameter $\alpha$ is equal to zero\footnote{This can be seen from Eq.~\ref{def:snd_gen}. If $\alpha = 0$ then $\Phi\left(\frac{\alpha(y-\xi)}{\omega}\right) = \Phi(0) = 0.5$ and therefore $SN(y;\xi, \omega, 0) = \frac{1}{\omega} \phi\left(\frac{y-\xi}{\omega}\right)$ which is the density or a Normal distribution. Note that $\Phi(0) = 0.5$ because $\Phi(0)$ is the the probability that a standard Normal random variable is less than or equal than 0.}.
%
\begin{figure}[htbp]
   \centering
\includegraphics[height = 3in]{Skew_Normal_densities_jjck.pdf} 
   \caption{Density function of a random variable Y following the SN distribution $SN(\xi, \omega^{2}, \alpha)$ with location parameter $\xi = 0$, scale parameter $\omega = 1$ and different values of the skewness parameter $\alpha$ indicated by different colors and line types. Note that the solid black line has an $\alpha = 0$, making it a Normal distribution.}
   \label{fig:SN.plot}
\end{figure}
%
For reasons related to the interpretation of the parameters in Eq.~\ref{def:snd_gen} and computational issues with estimating $\alpha$ near 0, a different parametrization is used in this work, which is referred to as the \emph{centered parametrization} (CP).  This CP is much closer to the parametrization of a Normal distribution, as it uses a mean parameter $\mu$, a variance parameter $\sigma^2$ and a skewness parameter $\gamma$. In order to define the CP, we need to express the CP parameters $(\mu, \sigma^2, \gamma)$ as a function of $(\xi, \omega^2, \alpha)$. This can be done using the following relations:
%
\begin{equation} \label{eq:snd_cp}
\mu = \xi + \omega \beta, \quad \sigma^{2} = \omega^{2}(1-\beta^2), \quad \gamma = \frac{1}{2}(4-\pi) \beta^{3}\left(1-\beta^2\right)^{-3/2},
\end{equation}
%
where $\beta = \sqrt{\frac{2}{\pi}}\left(\frac{\alpha}{\sqrt{1+\alpha^2}}\right)$ \citep[e.g.][]{Arellano-2010}.

By using Eq.~\ref{eq:snd_cp}, the new set of parameters $(\mu, \sigma^2, \gamma)$ provides a more clear interpretation of the behavior of the SN distribution. For the $\alpha$ values used in Fig.~\ref{fig:SN.plot}, the corresponding values of ($\mu$, $\sigma^2$, $\gamma$) are displayed in Table~\ref{tab:cp_values}.  In particular, $\mu$ and $\sigma^2$ are the actual mean and variance of the distribution, rather than simply a location and scale parameter, and $\gamma$ becomes an variable that evaluate the skewness of the SN.

Beyond the mean of the SN, we introduce a second location parameter that will be largely used in the analyses: the median. The median of the SN, and in general the median of an absolute continuous random variable, is defined as the value $m$ such that\footnote{We recall that when using a symmetric distribution such as the Normal distribution, the mean and the median are equivalent.}:
%
\begin{equation} \label{eq:snmed}
\int_{-\infty}^{m} SN(y;\xi, \omega, \alpha) = \frac{1}{2}.
\end{equation}
%

%% Requires the booktabs if the memoir class is not being used
\begin{table}[htbp]
   \centering
   %\topcaption{Table captions are better up top} % requires the topcapt package
   \begin{tabular}{|cccc|} % Column formatting, @{} suppresses leading/trailing space
\hline
$\alpha$ & $\mu$ & $\sigma^2$ & $\gamma$ \\
\hline
 -3 	&	 -0.757	&	 0.427	&	 -0.667 \\
0	&	 0.000 	&	1.000	&	 0.000 \\
2	&	 0.714	&	 0.491	&	 0.454\\
6	&	 0.787	&	 0.381	&	 0.891\\
10	&	 0.794	&	 0.370	&	 0.956\\
\hline
   \end{tabular}
   \caption{CP values $(\mu, \sigma^2, \gamma)$ corresponding to the $\alpha$ values shown in Fig.~\ref{fig:SN.plot}, with location parameter $\xi = 0$ and scale parameter $\omega = 1$. Values are rounded to three decimal places.}
   \label{tab:cp_values}
\end{table}
%
Further details about the parametrization from Eq.~\ref{def:snd_gen}, called \emph{Direct Parametrization} or DP, the CP, and general statistical properties of the SN are treated in rigorous mathematical and statistical viewpoints in the book by \cite{Azzalini2014}.

@@

%The CCF represents the average shape of spectral lines and is expressed in flux as a function of radial-velocity.
To fit the CCF using a SN distribution, we use a least-squares algorithm and the following model:
%
\begin{eqnarray} \label{eq:3}
f_{CCF}(y_i) = \mathrm{C} - \mathrm{A} \times SN(y_i;\mu, \sigma^2, \gamma), \quad i = 1, \ldots, n
\end{eqnarray}
%
where C is an unknown offset fitting for the continuum of the CCF, A is the unknown contrast of the CCF and $\mu$, $\sigma^2$ and $\gamma$ are the mean, variance and skewness of the SN as defined is Sect. \ref{sec:2}.
The values $y_1, \ldots, y_n$ are the different values of the abscisse of the CCF, generally with the dimension of a velocity.

Since the CCF presents a natural asymmetry due the convective blueshift, the SN distribution should in principle better catch this aspect, together with other changes in asymmetry, with respect to fitting a Normal distribution. To initially check this intuition, we compared the CCF residuals after fitting a Normal and a SN distribution for 2 stars. The first star is Alpha Centauri b, whose CCF's have high signal-to-noise ratio (SNR). The second star is Corot-7, whose CCF's have low SNR. Fig.~\ref{fig:Residual.comparison} shows that the SN seems to be a slightly better model to explain the shape of the CCF.%, in particular as the SNR decreases.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 2.5in]{[1]HD128621Residuals.pdf} 
\includegraphics[height = 2.5in]{[1]LRa01_E2Residuals.pdf} 
   \caption{Comparison between the Normal (black circles) and the SN (red crosses) residuals using CCF's from the star Alpha Centauri b (left) and Corot-7 (right). When looking at the residuals corresponding to the center of the CCF, the SN fit leads to slightly better results for both stars.} %Moreover, as the SNR decreases, the SN distribution shows smaller residuals respect the Normal ones.}
    \label{fig:Residual.comparison}
\end{figure*}
%

When fitting a Normal distribution to the CCF, the mean of the fitted distribution is defined as the measured RV, the FWHM of the Normal distribution ($=2\sqrt(2\ln2)\sigma$) represents the width of the CCF and because the Normal distribution is symmetric, a  skewness parameter cannot be obtained directly from this fit. Such a parameter is generally obtain in a second step by calculating the BIS SPAN of the CCF \citep[see Sect. \ref{intro}, and e.g.][]{Queloz-2001}. When fitting a SN distribution, we define two indicators for the RV: the mean of the SN, defined as SN mean RV and the median of the SN, defined as SN median RV. We will discuss advantages and limits for both of these choices in Sec. \ref{sec:4} and Sec. \ref{sec:5}. We define the width of the SN, SN FWHM, in the same way as for the Normal distribution\footnote{Note that SN FWHM does not correspond to the width of the SN distribution at half maximum like in the Normal case.}, and finally the skewness of the CCF, SN GAMMA, is derived using the $\gamma$ parameter.

To test the strength of the correlation between the estimated RV's and the different indicators used to evaluate stellar activity, we calculated the Pearson correlation coefficient, which in its general form is defined as:
%
\begin{equation}
R (x,y)= \frac{cov(x,y)}{\sigma(x),\sigma(y)},
\label{eq:Pearson:corr}
\end{equation}
%
where $x$ and $y$ are two quantitative variables, $cov(x,y)$ indicates the covariance between $x$ and $y$, and $\sigma(x)$ and $\sigma(y)$ represent their standard deviations.  A $p-$value for the statistical test having null hypothesis $H_{0}: R=0$ is provided, along with a $95\%$ confidence interval for $R$ when needed.

@@

While the parameters BIS SPAN and FWHM have already been introduced and used in \citep{Dumusque:2017aa,Feng:2017aa}, by using Eq.~\ref{eq:RV:correction} we propose also to include the contrast parameter $A$ and a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN WHM). The inclusion of the contrast parameter $A$ is justified by the expected behavior of the CCF in presence of active regions. Fig.~\ref{fig:spotA} shows that the presence for instance of a spot produces also changes in the amplitude of the CCF and not only on its asymmetry or width.
%
\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{FTS_solar_CCFs_whyWeAddAlsoPARAM_A.pdf} 
   \caption{The presence of a spot on the photosphere of a star produces changes on the amplitude of the CCF (also known as contrast) and not only on its asymmetry or width. This very same plot has been originally presented by \citep{Dumusque-2014b} when introducing the Spot Oscillation And Planet (SOAP) 2.0 simulator.}
    \label{fig:spotA}
\end{figure*}
%

The reasons for including in Eq.~\ref{eq:RV:correction} a variable that quantifies the interaction between BIS SPAN (or $\gamma$) and FWHM (or SN FWHM) will be better justified through the results of the examples presented in Sec.\ref{sec:soap}. We point out however that while the association between in this case BIS SPAN  (or $\gamma$) and FWHM (or SN FWHM) means that the values of one variable relate to the values of the other (since in this case we have two quantitative variables we talk about correlation), with the term interaction we mean that the effect that one variable has on the RV's is not constant. In particular the effect differs at different values of the other values. %As a consequence of this, if two variables are interacting the may or may not be associated.

@@

As final remark we recall that, when working with a linear regression, there are several ways to select the variables to include in the model. While usually the stepwise technique takes place \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction} that corrects from stellar activity is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it were the case, the matrix needed to calculate the estimates would have been singular, hence non invertible. This problem is known in statistic with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citep{belsley1991}. In the literature there are examples of stars presenting a high correlation between the contrast parameter $A$ and the FWHM \citep{Dumusque:2017aa,Feng:2017aa}. In the analyses of the presented work, we did not find any correlation between the contrast parameter $A$ and the FWHM (or between the contrast parameter $A$ and the SN FWHM) exceeding $0.66$ for all the analyzed stars and therefore the problem of multicollinearity is avoided. For the interpretation of the coefficients, we centered on the mean all the variables considered in the linear regression defined in Eq.~\ref{eq:RV:correction}. Last, when proposing interactions between covariates, we found that only the one between the width and the asymmetry of the CCF is statistically helpful to explain spurious variations in RV's caused by stellar activity. Consequently, in the present work, the interaction between other variables are not used as covariates.

%-----------------------------------------------------------------------------------------------------------------------------------------------
\section{Simulation Study} \label{sec:soap}
In order to evaluate the performance of the proposed SN approach for modeling the CCF and the goodness of the proposed correction from stellar activity by using Eq.~\ref{eq:RV:correction}, we begin by considering a simulation study using spectra generated from the Spot Oscillation And Planet (SOAP) 2.0 code \citep{Dumusque-2014b}.

@@

Since all the variations in RV's displayed in Fig.~\ref{fig:faculae} are caused by the presence of a faculae on the photosphere of the star, we corrected the originally estimated set of RV's by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the parameters involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. It is straightforward noticing that the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the faculae. In particular the $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN). We note also that the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM) is not statistically significant to explain spurious variations caused by a faculae.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{FACULAE_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of spurious variations in RV's caused by a faculae using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:faculae.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.0016$    & $0.26$ & $0.60$ \\
\hline
$\beta_{1}$            &    $3.75e-05$    & $0.0068$ & $0.0069$ \\
\hline
$\beta_{2}$            &     $7.79e-16$   &  $1.97e-05$ & $3.69e-08$\\
\hline
$\beta_{3}$            &     $0.25$   &  $0.0011$ & $0.0011$\\
\hline
$\beta_{4}$            &     $0.53$   &  $0.21$ & $0.21$\\
\hline
$R^{2}$      &     $0.9967$    &  $0.9571$ & $0.977$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a faculae, according to Eq.~\ref{eq:RV:correction}. Beyond the contrast parameter A and the asymmetry parameter of the CCF which are useful for both the analyses, the width of the CCF is statistically useful to explain spurious variations in RV's caused by a faculae only for the SN analyses. The term of interaction between the asymmetry and the width of the CCF is not helpful to explain part of the variability in the set of RV's. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
\label{table:faculae.test}
\end{table}

@@

As before, we corrected the originally estimated set of RV's by using Eq.~\ref{eq:RV:correction}. The results of the correction are displayed in Fig.~\ref{fig:spot.correction} and the statistical tests on the parameters involved in Eq.~\ref{eq:RV:correction} are summarized in Table \ref{table:spot.test}. Also in this case the proposed correction almost completely addresses the issue, providing a new set of RV's where there are not anymore spurious variations caused by the presence of the spot. The $R^{2}$ is extremely high regardless the fit that has been use (Normal or SN). The main differences respect to the previous case are that the parameter $\beta_{3}$, associated with $\gamma$, and the parameter $\beta_{4}$, associated with the interaction between $\gamma$ and SN FWHM (or BIS SPAN and FWHM), are statistically significant to explain spurious variations caused by a spot. This information could be useful in the future for disentangle spots from facuale.

\begin{figure*}[htbp]
   \centering
\includegraphics[height = 4in]{Spot_NEW_CORRECTION_[3]CorrectionActivity_RadialVelocity_vs_time.pdf} 
   \caption{Set of  spurious variations in RV's caused by a spot using a Normal and a SN fit before and once corrected from stellar activity. The correction is done using Eq.~\ref{eq:RV:correction} and the estimated parameters are presented in Table \ref{table:faculae.test}. Once corrected for stellar activity the residuals do not show a systematic component.}
    \label{fig:spot.correction}
\end{figure*}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Parameter          & RV         &   SN mean RV &   SN median RV \\
\hline
$\beta_{0}$            &    $0.47$    & $0.84$ & $0.81$ \\
\hline
$\beta_{1}$            &    $0.00035$    & $0.064$ & $0.064$ \\
\hline
$\beta_{2}$            &     $2e-16$   &  $2e-16$ & $2e-16$\\
\hline
$\beta_{3}$            &     $0.53$   &  $0.61$ & $0.61$\\
\hline
$\beta_{4}$            &     $1.11e-07 $   &  $2.85e-08 $ & $ 2.87e-08 $\\
\hline
$R^{2}$      &     $0.9897$    &  $0.9914$ & $0.9929$  \\
\hline
\end{tabular}
\caption{Evaluation of the linear combination used for correcting the RV's from spurious variations caused by a spot, according to Eq.~\ref{eq:RV:correction}. All the covariates are statistically useful to explain the variability in RV's causued by a spot except the intercept and the width of the CCF. Concerning the SN analysis, the contrast parameter A is not statistically significant at level $5\%$. The estimated $R^{2}$ show that the proposed correction for stellar activity explains all the spurious variability in RV's.}
\label{table:spot.test}
\end{table}
